### 2014-01-27 paper/chemokine_supplement.tex
Plos ONE Submission

\subsection{T Cell Production Rate}

To find a value for $\sigma$, the rate of production of activated T cells (ATCs) we use a differential equation model from \cite{Miao2010}:

{\footnotesize
\begin{equation*}
\label{EqS2}
\begin{aligned}
\dot{N_{c}} &= \sigma - \frac{r'^{2} \cdot N_{c}}{R^{2} \cdot t_{rc}}    & \pi r'^{2} &= a \sqrt{I} + b \\
\dot{N'_{f}} &= \frac{(r'^{2} - r^{2}) \cdot N_{c}}{R^{2} \cdot t_{rc}} - \frac{v_{tcell}}{(r' - r) / 2} \hspace*{2cm}  & \pi r^{2} &= \pi r_{cell}^{2} \cdot I \\
\dot{N_{f}} &= \frac{r^{2} \cdot N_{c}}{R^{2} \cdot t_{rc}} + \frac{v_{tcell}}{(r' - r) / 2} \\
\dot{T} &= \rho T -\beta TV \\
\dot{I} &= \beta TV - \delta I - k_{e} N_{f} I \\
\dot{V} &= pI - \beta TV - \gamma (t) V \\
\gamma (t) &= \left\{ \begin{array}{rcl}
	1/\mbox{day} & \mbox{,}  & t < 5  \\
	3/\mbox{day} & \mbox{,} & t \geq 5  
	\end{array}\right. \\
\end{aligned}
\tag{\textbf{S}1}
\end{equation*}
}
\vspace{.05in}

where $N_{c}$ is the number of circulating activated antigen-specific T cells, $N'_{f}$ is the number of circulating T cells that have found and exit into a region of lung tissue expressing chemokines and $N_{f}$ is the number of circulating T cells that have found an infected region. $T$ is the number of uninfected target cells, $I$ is the number of productively infected cells, and $V$ is the viral titer in serum. The infected region is assumed to be of radius $r$ and is within a region expressing chemokines of radius $r'$ ($r  < r'$). The lung is assumed to be a circular region with radius $R$. The area of the infected region is equal to the area of an infected cell (of radius $r_{cell}$) multiplied by the number of infected cells. See Fig. 1 for more details about the model.  The area of the region expressing chemokine was found to be related non-linearly to the number of infected cells ($\pi r'^{2} = a \sqrt{I} + b$) where $a$ and $b$ are constants that depend on the viral strain.

Circulating activated antigen-specific T cells ($N_{c}$) are assumed to be released from lymph nodes at a constant rate $\sigma$ and circulate to the $N'_{f}$ population over a time defined by $t_{rc}$. These circulating cells transition into $N'_{f}$ and $N_{f}$ at rates proportional to the areas of the chemokine expressing and infected regions relative to the whole lung area. Circulating cells that are in the chemokine expressing region ($N'_{f}$) transition to the infected region after walking randomly for an average time proportional to the difference in the radii between the two regions ($r' - r$) at a given speed, $v_{tcell}$. Target cells ($T$) become infected by virus at rate $\beta TV$, where $\beta$ is the rate constant characterizing infection. Infected cells ($I$) die at rate $\delta$ in addition to being lysed by T cells ($N_{f}$) at a rate $k_{e}$. Finally the viral titers ($V$) increase due to production of virus at rate $p$ by infected cells. Virus is also cleared due to uptake by infected cells (at a rate $- \beta TV$) and due to antibody (at a rate $\gamma (t)$ that changes after 5 days post infection). The initial viral titer was initialized to 10,000 PFUs and the initial number of target cells was one million. The initial number of infected cells is assumed to be zero. This ODE was fit to data taken from \cite{Miao2010} using Matlab's \texttt{nlinfit} function in order to obtain a value for $\sigma$.  The final value was found to be 777 per hour.

\subsection{CyCells Implementation Details}

The CyCells modeling environment splits its populations into two types: cells and molecules.  Cells are considered to be unique agents and are modeled individually.  On the other hand, molecules are considered to be too small and numerous to model explicitly and are thus represented as compartmentalized concentrations.  These compartments are arranged as a grid that covers the environment.  Each square in the grid contains a unique concentration of the given molecule.  Multiple molecules are represented in separate grids.

@@

New molecules can be secreted by cell objects, such as an infected cell secreting new virus.  In this scenario CyCells calculates the amount of virus secreted per time step, based upon the cell's defined production rate, and then adds this quantity to the grid square that overlaps the secreting cell.  If a cell wants to remove molecular concentration, it will subtract from the square it overlaps.  If the concentration at that square is not enough, concentration will be removed from neighboring squares in an ever expanding diamond.

When a cell's behavior depends on a local molecular concentration, the cell will measure the local concentration at its position by calculating a linearly interpolated combination of the concentrations in the grid squares surrounding the cell.

\subsection{Model Implementation Details}

An overview of the model implementation is shown in Fig. 2.  The model is initialized with one virus-secreting cell placed in the middle of a 2-dimensional sheet of hexagonally-tiled epithelial cells (46,085 total cells).  The sheet measures 10$mm$ per side, which is large enough to contain the infection (Fig. 5).  The molecular grid (S1.2) is initialized with a resolution of 50$\mu m$.

@@

Virus-secreting cells secrete both virus and chemokine (the RANTES portion of the chemokine production is added in 16 hours after the initial infection) and die after 1,000 minutes of production (16.7 hours).  Virus-secreting cells will also probabilistically transition to apoptizing cells in the presence of T cells (defined by the existence of a T cell within 5$\mu m$).  The number of T cells in the vicinity of the virus-secreting cell has no effect on the rate that apoptosis is induced in the model.

Apoptizing cells continue to secrete virus and chemokine for one hour and then die.

T cells are added to the model at a constant rate of 777 per hour (S1.1) through a global `oracle' cell that represents the lymph node.  Because the model environment is only a small portion of the entire lung (1\%), most of the T cells miss the model window and are not visually represented.  The T cells that miss enter a dormant searching state and transition to recirculating after a 10 minute delay.  The cells that enter the model window are placed at a random position and begin a random walk.  At each step, these searching cells check the local chemokine concentration.  If the concentration is above the sensitivity threshold, the T cells immediately transition to the chemotaxing state.  If not, searching T cells transition to the recirculating state and are removed from the model window.  Searching and recirculating T cells have a probabilistic decay rate that corresponds to a 3 day lifespan.

Recirculating T cells are not visually represented.  These cells are individually tracked for 6 minutes, after which they are reintroduced as new searching cells with a new chance of entering the model window.

Chemotaxing T cells move directly up the chemokine gradient until they find a local maximum.  T cells probabilistically decay at a rate corresponding to a 2 hour lifespan.  Chemotaxing T cells have no effect other than inducing apoptosis in virus-secreting cells by proximity.

@@

\subsection{Stochastic modeling effects}

Unlike ODE models, which are deterministic, stochastic models such as CyCells can produce different results on different runs (Fig.~S\ref{fig:variance}).  To test the strength of this effect, we ran each model fifty times using the default parameters given in Table 2.  $R^2$ values were calculated for individual runs versus the average of all runs.  Pandemic H1N1 showed the least inter-run variance with an mean $R^2$ value of 0.9935 and standard deviation of 0.0029.  sH1N1 had a mean $R^2$ 0.9859 with a standard deviation of 0.0109.  aH5N1 had a mean $R^2$ of 0.9167 with a standard deviation of 0.0726.

Each run took the calculated viral production and chemokine production rates for the three different strains of influenza as input and reported the total number of infected cells, including incubating, virus secreting and apoptotic, but not including dead cells.  Therefore the figures approximate plaque growth over time.

Overlaying multiple runs on a single plot reveals a slight growth rate transition 3 days p.i., which reflects the addition of IgM.  In addition, for each infection the number of infected cells declines quickly at day five due to the T cell response.

The three strains show different levels of virulence, consistent with the results found in \cite{Mitchell2011} (Fig.~S\ref{fig:variance}).  The rapid production of the pandemic H1N1 virus prevents the immune response from containing the infection.  Because pH1N1 is replicates at such a rapid rate, the window of opportunity for T Cells to gain ground is too small.  aH5N1 is cleared completely, sH1N1 is contained but not fully cleared, and pH1N1 recovers and continues to expand.

@@

Four models runs were performed for each strain (two for aH5N1) to look at how the presence and/or lack of specific chemokines affect the simulated immune response (Fig.~S\ref{fig:chemokine}).  The lack of both chemokines leads to runaway infections in all three strains.  The presence of only RANTES is enough to contain the aH5N1 infection, but is weaker than IP-10 in both H1N1 strains.  In sH1N1 and pH1N1 simulations, IP-10 alone proves to be as effective as the combination of IP-10 and RANTES.  This suggests that RANTES does not play a significant role in infections that stimulate an IP-10 response due to the higher production rates of IP-10.

@@

\begin{figure}[ht!]
\begin{center}
% \includegraphics[width=\textwidth]{variance}
 \end{center}
\caption{Model results: Time series plots of fifty runs of aH5N1 (A), sH1N1 (B), and pH1N1 (C) infections (gray). IP-10 and RANTES were simulated in each run, except for aH5N1, which  produced only RANTES.  Each run was initialized identically for each strain save for the random seed.  The middle line shows the average while the outer lines show the 95\% confidence interval.} 
 \label{fig:variance}
\end{figure}

\begin{figure}[ht!]
\begin{center}
%	\includegraphics[width=\textwidth]{chemokine}
	\caption{Effects of different chemokine combinations.  A) aH5N1 does not stimulate an IP-10 response.  B-C) sH1N1 and pH1N1 show no significant difference between IP-10 alone versus IP-10 and RANTES combined.}
	\label{fig:chemokine}
\end{center}
\end{figure}

@@

\begin{figure}[ht!]
\caption{A closer look at the 2009 pandemic simulation.  This video shows the infection from day 6 to day 7 with each frame spanning 100 simulated seconds.  Healthy cells are gray, virus-incubating cells are yellow, virus-secreting cells are orange, apoptotic cells are red, and T cells are green.  Note the high proportion of virus-secreting cells (orange) early on.  As time passes, secreting cells are gradually contained to the point where they become very sparse.  T cell clumping often prevents the T cells from quick discovery of new secreting cells.}
\end{figure}

@@

%\begin{table}[!ht]
%\caption{
%\bf{Table title}}
%\begin{tabular}{|c|c|c|}
%table information
%\end{tabular}
%\begin{flushleft}Table caption
%\end{flushleft}
%\label{tab:label}
% \end{table}

\begin{table}[!ht]
\begin{center}
\begin{tabular}{ | c | c | c | }
  \hline                        
  Paramter & Value & Source \\
  \hline
  T(0) & $1e6$ & \cite{Mitchell2011} \\
  V(0) &  $1e4$ & \cite{Mitchell2011} \\
  $r_{cell}$ &  $10 \mu m$ & \cite{Miao2010} \\
  $t_{rc}$ & $6s$ & \cite{Peters1983} \\
  $v_{tcell}$ & $0.3 \mu m/s$ & \cite{Miller2003} \\
  $k_e$ & $6.4e-5/cell/day$ & \cite{Miao2010} \\
  $\beta$ & $4.8e-7/cell/PFU$ & \cite{Mitchell2011} \\
  $p$ & $0.18 PFU/h$ & \cite{Mitchell2011} \\
  $\delta$ & $16.7 hours$ & \cite{Mitchell2011} \\
  $a$ & $20.9$ & ABM fits \\
  $b$ & $70.8$ & ABM fits \\
  \hline  
\end{tabular}
\caption{Supplemental model parameters.  Most values are chosen to match the equations borrowed from both \cite{Mitchell2011} and \cite{Miao2010}.  Values \textit{a} and \textit{b} were fit to multiple runs of a simplified CyCells ABM.}
\label{table:supplement}
\end{center}
\end{table}

>>>>

\subsection{Estimating chemokine production rates}

We estimate chemokine production rates, `r', by adapting the delay differential equation model of influenza infection described in \cite{Mitchell2011} \drew{Eq. 1} by adding one new equation ($\dot{C}=r I_{1 \tau_3}-dC$) to model chemokine production.  Initial population sizes and parameter values are taken from the previous study.
{\footnotesize
\begin{equation}
\begin{aligned}
\dot{T} &= - \beta T V \\
\dot{I_1} &= \beta T V - \beta T_{\tau_1}V_{\tau_1} \\
\dot{I_2} &= \beta T_{\tau_1}V_{\tau_1} - \delta I_2 \\
\dot{V} &= \frac{p}{1+eF} I_2  - \beta T V  \\
\dot{F} &=  I_{1 \tau_2} \\
\dot{C} &= r I_{1 \tau_3} - d C \\
\end{aligned}
\label{eq:dde}
\end{equation}
\vspace{.05in}
}

$\tau$ subscript variables denote delay terms, signifying the value is the population quantity in existence at time $t - \tau$.  Table 1 summarizes population and parameter values and descriptions.  Strain-specific values for $r$ were found by fitting the equations to experimental data (see Results and Table 3).

\subsection{T cell production rate}

We calculate the rate of production ($\sigma$) of CD8 T cells using a differential equation model from \cite{Miao2010}.  The equations model T cell production and subsequent search over an area of infected lung tissue.

{\footnotesize
\begin{equation*}
\label{EqS1}
\begin{aligned}
\dot{N_{c}} &= \sigma - \frac{r'^{2} \cdot N_{c}}{R^{2} \cdot t_{rc}} & \pi r'^{2} &= a \sqrt{I} + b \\
\dot{N'_{f}} &= \frac{(r'^{2} - r^{2}) \cdot N_{c}}{R^{2} \cdot t_{rc}} - \frac{v_{tcell}}{(r' - r) / 2} \hspace*{2cm}  & \pi r^{2} &= \pi r_{cell}^{2} \cdot I \\
\dot{N_{f}} &= \frac{r^{2} \cdot N_{c}}{R^{2} \cdot t_{rc}} + \frac{v_{tcell}}{(r' - r) / 2} \\
\dot{T} &= \rho T -\beta TV \\
\dot{I} &= \beta TV - \delta I - k_{e} N_{f} I \\
\dot{V} &= pI - \beta TV - \gamma (t) V \\
\gamma (t) &= \left\{ \begin{array}{rcl}
	1/\mbox{day} & \mbox{,}  & t < 5  \\
	3/\mbox{day} & \mbox{,} & t \geq 5  
	\end{array}\right. \\
\end{aligned}
\tag{S1}
\end{equation*}
}
\vspace{.05in}

$N_{c}$ is the number of circulating activated antigen-specific CD8 T cells, $N'_{f}$ is the number of circulating T cells that have found and exit into a region of lung tissue expressing chemokines, $N_{f}$ is the number of circulating T cells that have found an infected region. $T$ is the number of uninfected \textit{target} cells, $I$ is the number of productively infected cells, and $V$ is the viral titer in serum. The infected region is assumed to be of radius $r$ and is within a region expressing chemokines of radius $r'$ ($r  < r'$). The lung is modeled as a circular region with radius $R$. The area of the infected region is equal to the area of an infected cell (of radius $r_{cell}$) multiplied by the number of infected cells. See Fig. 1 for more details about the model.  The area of the region expressing chemokine was found to be related non-linearly to the number of infected cells ($\pi r'^{2} = a \sqrt{I} + b$) where $a$ and $b$ are constants that depend on the viral strain.  $a$ and $b$ were fit using 12 experimental runs of a spatial model implemented in CyCells.

Circulating CD8 T cells ($N_{c}$) are assumed to be released from lymph nodes at a constant rate $\sigma$ and circulate to the $N'_{f}$ population over a time defined by $t_{rc}$. We assume these circulating cells transition into $N'_{f}$ and $N_{f}$ at rates proportional to the areas of the chemokine expressing and infected regions relative to the whole lung area.

The average time an exiting CD8 T cell takes to migrate to the infected region is equal to the difference in the radii between the two regions ($r' - r$) times the T cell speed, $v_{tcell}$.  Circulating cells that are in the chemokine expressing region ($N'_{f}$) move into the infected region after performing chemotaxis for that time. Target cells ($T$) become infected by virus at rate $\beta TV$, where $\beta$ is the rate constant characterizing infection. Infected cells ($I$) die at rate $\delta$ in addition to being lysed by T cells ($N_{f}$) at a rate $k_{e}$. Finally the viral titers ($V$) increase due to production of virus at rate $p$ by infected cells. Virus is also cleared due to uptake by infected cells (at a rate $- \beta TV$) and due to antibody (at a rate $\gamma (t)$ that changes after 5 days post infection). The initial viral titer was initialized to 10,000 PFUs and the initial number of target cells was one million. The initial number of infected cells is assumed to be zero. Parameter values are listed in Table S1 in Text S1.  This ODE was fit to data taken from \cite{Miao2010} using Matlab's \texttt{nlinfit} function in order to obtain a value for $\sigma$.  The final value was found to be 1,257 per hour.

\subsection{CyCells implementation details}

The CyCells modeling environment splits its populations into two types: cells and molecules.  Cells are considered to be unique agents and are modeled individually.  Conversely, molecules are represented as compartmentalized concentrations.  These compartments are arranged as a grid that covers the environment.  Each square in the grid contains a unique concentration of the given molecule.  Each type of  molecule is represented in a unique grid.

@@

New molecules can be secreted by cell objects, such as an infected cell secreting new virus.  In this scenario CyCells calculates the amount of virus secreted per time step, based upon the cell's defined production rate, and then adds this quantity to the grid square that overlaps the secreting cell.  If a cell ingests a molecule, it will subtract the appropriate concentration from the grid square it overlaps.  If the concentration at that square is not enough to represent a full molecule, concentration will be removed from neighboring squares in an ever expanding diamond until the total concentration is equal to a single molecule.

Cells will measure the local concentration at their position by calculating a linearly interpolated combination of the concentrations in the grid squares surrounding the cell in instances where cell behavior depends on the local molecular concentration.

\subsection{Model implementation details}

An overview of the model implementation is shown in Fig. 2.  The model is initialized with one virus-secreting cell placed in the middle of a 2-dimensional sheet of hexagonally-tiled epithelial cells (288,212 total cells).  The sheet measures 5$mm$ per side, which is large enough to contain the infection (Fig. 5).  The molecular grid (Text S1 1.3) is initialized with a resolution of 20$\mu m$.  Each time step of the model represents 6 seconds.

@@

Virus-secreting cells secrete both virus and chemokine (the RANTES portion of the chemokine production is added in 16 hours after the initial infection) and die after 1,000 minutes of production (16.7 hours).  Virus-secreting cells will also probabilistically transition to apoptizing cells in the presence of T cells (defined by the existence of a T cell within 2$\mu m$).  The number of T cells in the vicinity of the virus-secreting cell has no effect on the rate that apoptosis is induced in the model.

Apoptizing cells secrete virus and chemokine for one hour and then die.

T cells are added to the model at a constant rate of 1,257 per hour (Text S1 1.1).  Because the model environment is only a small portion of the entire lung (0.25\%), most of the T cells miss the model window and are not visually represented.  The T cells that miss recirculate and enter the lung at a new random location after a delay of six seconds.

The cells that enter the model window are placed at a random position and immediately check the local chemokine concentration.  If the concentration is above the sensitivity threshold, the T cells immediately transition to the chemotaxing state.  If not, the T cells recirculate and reenter the lung in a new location after a six second delay.  Recirculating T cells have a probabilistic decay rate that corresponds to a 3 day lifespan.  Recirculating T cells are not visually represented.

Chemotaxing T cells move directly up the chemokine gradient until they find a local concentration maximum.  T cells probabilistically decay at a rate corresponding to a 2 hour lifespan.  Chemotaxing T cells have no effect other than inducing apoptosis in virus-secreting cells by proximity.

\subsection{Modeling Decisions}

\subsubsection{Two dimensional lung}

We model the lung as a two-dimensional system for several reasons.  Unlike the lymph node where dendritic cells and T cells navigate a three-dimensional volume, lung infection dynamics are confined to a thin tissue between capillary endothelial cells and alveolar epithelial cells.  Although these alveoli are segregated by the lung's acinar structure on a small scale, we do not represent this in the model because the spreading of influenza eventually ignores the boundaries between acinii.  Therefore our model does not incorporate this small-scale level of segregation.

\subsubsection{Uniform blood flow}

Our model assumes that blood flows uniformly through the lung vascular network.  It is possible that blood flow is increased in the direction of an infected region of the lung by local inflammation.  Thus our model may underestimate the recruitment efficiency of local inflammation and hyperemia.  If this is indeed the case, our model underestimates the effect of the immune response.

%\subsubsection{T cell velocity}
%\fred{T cell velocity in the lung is extremely difficult to measure.} \removed{Little is known of T cell chemotaxis speed in the lung.}  We give chemotaxing T cells a velocity of $3\mu m/s$ and T cells that are performing a random walk a velocity of $30\mu m/s$.  \removed{These values are faster that speeds found in other organs, such as the lymph node.  This is reasonable because T cells in the lung travel on top of a packed surface without needing to navigate through blood flow.  Furthermore, T cell speed has little effect on the model behavior as detailed below (S2.3).}  \fred{These rapid values estimate velocity of capillary blood flow in the extensive network of capillaries beyond the 14th bifurcation of the lung arterial system.  T cell velocity would be expected to be slower within interstitial tissue, but this was not modeled in most simulations.  In runs where velocity was varied over 5 orders of magnitude, including slow velocities measured in lymph node and skin by other authors, T cell velocity had little effect on model behavior and infection control as shown below (S2.3).}
%

%See Table~\ref{table:assumptions}.

@@

\subsection*{T cell sensitivity to chemokine}

The model simulates a chemokine gradient surrounding the infected focus (Fig. 5), based on the calculated per-infected cell secretion rate (Table 3) and known chemical parameters for a 10 kDa protein (Table 2).  T cell sensitivity depends on receptor density \cite{Desmetz2006} and this was assumed to be constant.

Because this parameter is unknown, we simulated T cell sensitivity levels ranging over 10 orders of magnitude.  Concentration-dependent behavior of cells responding to chemokine was the same over a wide range of concentrations from 0.01 pg/mL to 100 ng/mL (model variance is discussed in Text S1 2.1.).  Decreased recruitment was predicted only by supra-natural concentration sensitivity levels at and above 1 $\mu$g/mL.  We then set the sensitivity to 100 $ng/mL$ for all future runs (10 $nM$ concentration assuming a chemokine molecular weight of 10 $kDa$) \cite{Gao2003}.

% Because more than one T cell at each infected epithelial cell would not increasing effective target cell death, there may be a threshold of immigrant T cells above which no additional control of viral replication is possible.

@@

Four models runs (both, IP-10, RANTES, and none) were performed for sH1N1 and pH1N1 strains and two runs (RANTES and none) for  aH5N1.  The runs show how the presence and/or absence of specific chemokines affect the simulated immune response (Fig.~S\ref{fig:chemokine}).  The lack of both chemokines leads to runaway infections in all three strains.  The presence of only RANTES is enough to contain the aH5N1 infection, but is weaker than IP-10 in both H1N1 strains.  In sH1N1 and pH1N1 simulations, IP-10 alone proves to be as effective as the combination of IP-10 and RANTES.  This suggests that RANTES does not play a significant role in infections that stimulate an IP-10 response due to the higher production rates of IP-10.

%\drew{
%\subsection{T cell speed}
%
%\removed{T cell speed over bronchial epithelial cells is unknown.}\fred{T cell velocity within the capillary network and after diapedesis with the lung interstitial tissue is unknown.}  We tested values for T cell speed to measure the effect it had on the general infection dynamics (Fig.~S\ref{fig:speed}).  The results show that the difference in T cell speeds is small, although there does appear to be an discernible effect on the infection during \removed{the early phase of the T cell response} \fred{the initial appearance of activated T cell migration between days 5 and 7 post infection.}.
%}

@@

\setcounter{figure}{0}
\renewcommand{\thefigure}{S\arabic{figure}}

\begin{figure}[!ht]
\begin{center}
% \includegraphics[width=\textwidth]{Figure_S1}
 \end{center}
\caption{{\bf Varying T cell sensitivity to chemokine.}  H5N1 model results use RANTES  only, and sH1N1 and pH1N1 use both IP-10 and RANTES. Total number of incubating, secreting and apoptotic cells are plotted for each infection.  The sensitivity value specifies the minimum level of chemokine concentration required for T cells to detect it. } 
 \label{fig:sensitivity}
\end{figure}

\begin{figure}[ht!]
\begin{center}
%	\includegraphics[width=\textwidth]{Figure_S2}
	\caption{\textbf{Effects of different chemokine combinations.}  A) aH5N1 does not stimulate an IP-10 response.  B-C) sH1N1 and pH1N1 show no significant difference between IP-10 alone versus IP-10 and RANTES combined.}
	\label{fig:chemokine}
\end{center}
\end{figure}

%\begin{figure}[ht!]
%\begin{center}
%	\includegraphics[width=\textwidth]{Figure_S3}
%	\caption{\drew{\textbf{Effects of different T cell speeds.}  With the exception of sH1N1, T cell speeds show a small effect during the early phase of the T cell response.  After a time of approximately two days, the infection dynamics converge to a similar rate of growth across all speed values.}}
%	\label{fig:speed}
%\end{center}
%\end{figure}

\setcounter{figure}{0}
\renewcommand{\figurename}{Video}

@@

\begin{figure}[ht!]
\caption{A closer look at the 2009 pandemic simulation.  This video shows the infection from day 6 to day 7 with each frame spanning 1 simulated minute.  Healthy cells are gray, virus-incubating cells are yellow, virus-secreting cells are orange, apoptotic cells are red, and T cells are green.  Note the high proportion of virus-secreting cells (orange) early on.  As time passes, secreting cells are gradually contained to the point where they become very sparse.  T cell clumping often prevents the T cells from quick discovery of new secreting cells.}
\end{figure}

@@

%\begin{table}[!ht]
%\caption{
%\bf{Table title}}
%\begin{tabular}{|c|c|c|}
%table information
%\end{tabular}
%\begin{flushleft}Table caption
%\end{flushleft}
%\label{tab:label}

% \end{table}

\renewcommand{\thetable}{S\arabic{table}}

\begin{table}[!ht]
\begin{center}
\begin{tabular}{ | c | c | c | }
  \hline                        
  Paramter & Value & Source \\
  \hline
  T(0) & $1e6$ & \cite{Mitchell2011} \\
  V(0) &  $1e4$ & \cite{Mitchell2011} \\
  $r_{cell}$ &  $5 \mu m$ & \cite{Miao2010} \\
  $t_{rc}$ & $6s$ & \cite{Peters1983} \\
  $k_e$ & $6.4e-5/cell/day$ & \cite{Miao2010} \\
  $\beta$ & $4.8e-7/cell/PFU$ & \cite{Mitchell2011} \\
  $p$ & $0.18 PFU/h$ & \cite{Mitchell2011} \\
  $\delta$ & $16.7 hours$ & \cite{Mitchell2011} \\
  $a$ & $67.7$ & ABM fits \\
  $b$ & $433.5$ & ABM fits \\
  \hline  
\end{tabular}
\caption{Supplemental model parameters.  Most values are chosen to match the equations borrowed from both \cite{Mitchell2011} and \cite{Miao2010}.  Values \textit{a} and \textit{b} were fit to multiple runs of a simplified CyCells ABM.}
\label{table:supplement}
\end{center}
\end{table}

%\begin{table}[!ht]
%\begin{center}
%\begin{tabular}{ | c | c | }
%  \hline                        
%  Assumption & Description \\
%  \hline
%  2D hexagonal layout & The lung can be stretched flat.  T cells travel on the cellular surface. \\
%  Even blood flow to all capillaries & We assume that there is negligible increased blood flow to the infected region. \\
%  Rapid T cell circulation & Activated T cells in circulation do not spend time in new lymph nodes as they circulate. \\
%  T cell speed & T cells move at a rate of XXX in the absence of chemokine and XXXX once it detects chemokine. \\
%  T cell search time & T cells search in the lung for 6 minutes before they recirculate. \\
%  \hline  
%\end{tabular}
%\caption{Supplemental model parameters.  Most values are chosen to match the equations borrowed from both \cite{Mitchell2011} and \cite{Miao2010}.  Values \textit{a} and \textit{b} were fit to multiple runs of a simplified CyCells ABM.}
%\label{table:assumptions}
%\end{center}
%\end{table}

### 2014-01-27 paper/cover_letter.tex
Plos ONE Submission

We resubmit this manuscript entitled "Spatially explicit model of the lymphocyte diaspora in influenza-infected lung reveals thresholds on chemokine directed migration" for consideration of publication in PLoS Computational Biology.  We would like to thank each of you for giving us the opportunity to improve our paper and resubmit it.  We would like to reiterate our thanks to our reviewers for giving us very constructive criticism that we believe has greatly improved the paper.  We still feel this work will be of interest to investigators modeling the immune response for the ultimate purpose of improving vaccine design.  \\

@@

In review we have noticed that our bibliography does not use annotated journal names, which seem to be the standard for PLoS CB.  We have {\em not} changed our bibliography as of yet as it was generated automatically using the Mendeley Desktop suite.  If this is an issue, we would be happy to return and reconstruct the references manually. \\

>>>>

We submit this manuscript entitled "Spatially explicit model of the efficiency of the lymphocyte diaspora in influenza-infected lung reveals thresholds on chemokine directed migration" for consideration of publication in PLOS ONE.  Our paper implements an agent-based model of bronchial influenza infection and the subsequent T cell response using new empirical values of chemokine secretion.  The paper shows that chemokine levels have a limited yet important role in directing T cell migration and that the spatial effects of chemokine diffusion can actually hinder T cell search in rapidly spreading viruses.  We feel this work will be of interest to investigators modeling the immune response for the ultimate purpose of improving vaccine design.
 \\

@@

In review we have noticed that our bibliography does not use annotated journal names, which seem to be the standard for PLOS ONE.  We have {\em not} changed our bibliography as of yet as it was generated automatically using the Mendeley Desktop suite.  If this is an issue, we would be happy to return and reconstruct the references manually. \\

% This work is a resubmission of a rejected PLOS CB manuscript (PCOMPBIOL-D-12-01516R1).
